Proposal to improve BBC Search through the use of Linked Data

### 2014-05-02 paper.tex
Some reworking around bit on RDFa.

The Semantic Web movement has long recommended an approach of embedding
RDF data models within web pages and documents using RDFa\cite{adida2012rdfa}
and RDFa Lite\cite{lite2004rdfa}.

>>>>

Whilst there exist multiple formats for publishing RDF purely for machines
(e.g. Turtle\cite{world2014rdf}, N-Triples, JSON-LD\cite{world2014json},
N3, RDF/XML) there are multiple ways to embed semantic or linked data within
an HTML web page:

\begin{itemize}
  \item RDFa\cite{adida2012rdfa} and RDFa Lite\cite{lite2004rdfa}.
  \item DC-HTML defines how to embed the Dublin Core vocabulary within HTML
    meta tags.
\end{itemize}
